Guilt, shame, and anti-war action in an authoritarian country at war

### 2024-06-08 manuscript.Rmd
Trying with built in latex instead of tinytex

---
title: "Guilt, shame, and anti-war action in an authoritarian country at war"
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
    keep_tex: yes
    toc: no
  word_document:
    toc: no
  bookdown::word_document2:
    toc: no
  html_document:
    df_print: paged
always_allow_html: yes
test: "`r OS <- Sys.info()['sysname']`
`r if (OS=='Linux'){fontname <- 'Nimbus Roman'}`
`r if (OS=='Darwin'){fontname <- 'Times New Roman'}`
`r if (OS=='Windows'){fontname <- 'Times New Roman'}`"
header-includes:
- \usepackage{indentfirst}
- \usepackage{sectsty}
- \allsectionsfont{\centering}
- \usepackage{fontspec}
- \usepackage{polyglossia}
- \setdefaultlanguage{english}
- \setotherlanguages{russian}
- \setmainfont{`r fontname`}
- \newfontfamily{\cyrillicfonttt}{`r fontname`}
- \usepackage{float}
- \usepackage{float} \floatplacement{figure}{H}
- \newcommand{\beginsupplement}{\setcounter{table}{0}
- \renewcommand{\thetable}{S\arabic{table}}
- \setcounter{figure}{0}
- \renewcommand{\thefigure}{S\arabic{figure}}}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
indent: yes
bibliography: references.bib
csl: elife.csl
---

@@

# download latex if not already present
if (!tinytex::is_tinytex()){tinytex::install_tinytex(force = TRUE)}

>>>>

---
title: "Guilt, shame, and anti-war action in an authoritarian country at war"
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
    keep_tex: yes
    toc: no
  word_document:
    toc: no
  bookdown::word_document2:
    toc: no
  html_document:
    df_print: paged
always_allow_html: yes
test: "`r fontname <- 'Times New Roman'`
`r OS <- Sys.info()['sysname']`
`r if (OS=='Linux'){fontname <- 'Nimbus Roman'}`"
header-includes:
- \usepackage{indentfirst}
- \usepackage{sectsty}
- \allsectionsfont{\centering}
- \usepackage{fontspec}
- \usepackage{polyglossia}
- \setdefaultlanguage{english}
- \setotherlanguages{russian}
- \setmainfont{`r fontname`}
- \newfontfamily{\cyrillicfonttt}{`r fontname`}
- \usepackage{float}
- \usepackage{float} \floatplacement{figure}{H}
- \newcommand{\beginsupplement}{\setcounter{table}{0}
- \renewcommand{\thetable}{S\arabic{table}}
- \setcounter{figure}{0}
- \renewcommand{\thefigure}{S\arabic{figure}}}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
indent: yes
bibliography: references.bib
csl: elife.csl
---

@@

# download latex if not already present
# if (!tinytex::is_tinytex()){tinytex::install_tinytex(force = TRUE)}
